A weakly structured stem for human origins in Africa

### 2022-08-31 paper.tex

\begin{figure}[t!]
    \centering
    \includegraphics{figures/predictions.pdf}
    \caption{
        \textbf{Structure among stems is weak and present-day structure is mostly recent.}
        From the best fit models of our two parameterizations (A and B:
        continuous migration, C and D: merger with stem migration),
        we predicted pairwise differences $H_{i,j}$ between individuals
        sampled from populations $i$ and $j$ existing at time $t$ (A and C).
        (B and D) To understand how drift between stems explains contemporary structure, 
        we also computed the proportion $\alpha^2$ of drift between pairs of
        sampled contemporary
        populations that aligns with drift between past populations
        (here Nama and Mende, see Supp. Information Section~S\ref{sec:f4}
        for details and additional comparisons in
        Figures~\ref{fig:supp-f4s-single-origin}--\ref{fig:supp-f4s-merger-with-stem-migration}).
        Both models infer deep population structure with modest contributions to
        contemporary genetic differentiation.
        Most present differentiation dates back to the last 100ka.
    }
    \label{fig:predictions}
\end{figure}

>>>>

\begin{figure}[t!]
    \centering
    \includegraphics{figures/predictions.pdf}
    \caption{
        \textbf{Structure among stems is weak and present-day structure is mostly recent.}
        From the best fit models of our two parameterizations (A and B:
        continuous migration, C and D: merger with stem migration),
        we predicted pairwise differences $H_{i,j}$ between individuals
        sampled from populations $i$ and $j$ existing at time $t$ (A and C).
        (B and D) To understand how drift between stems explains contemporary structure, 
        we also computed the proportion $\alpha^2$ of drift between pairs of
        sampled contemporary
        populations that aligns with drift between past populations
        (here Nama and Mende, see Supp. Information Section~S\ref{sec:f4}
        for details and additional comparisons in
        Figures~\ref{fig:supp-f4s-single-origin}--\ref{fig:supp-f4s-merger-with-stem-migration}).
        Both models infer deep population structure with modest contributions to
        contemporary genetic differentiation.
        Most present differentiation dates back to the last 100ka.
    }
    \label{fig:predictions}
\end{figure}
To assess robustness of the inferred models to analysis and reference population choices, 
Sections \ref{sec:validation_strategy} and \ref{sec:validation_results} present re-analyses changing the European and West African populations, as well as the recombination maps, 
filtering strategies and parameter optimization strategies. While we find some differences in the inferred parameters (see in particular \ref{sec:replacing} and \ref{sec:change-dates}), the best fit model across all reanalyses are quantitatively consistent.
